---
title: "Authoring ILIAS-ready questions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Authoring ILIAS-ready questions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This article summarizes the authoring patterns currently covered by the package
and its bundled examples.

## Supported exercise types

The package exports the following main question types:

- `cloze`
- `schoice`
- `mchoice`
- `num`
- `string`

For cloze exercises, the gap subtypes `num`, `string`, `schoice`, and
`mchoice` are mapped to the corresponding ILIAS gap elements.

## Recommended cloze style

For new cloze exercises, the recommended style is to use
`exams::add_cloze()` together with `format_metainfo()`. This keeps the
question text and the cloze metadata synchronized.

```{r}
library(exams)

n <- sample(20:30, 1)
mean_x <- sample(seq(70, 80, by = 0.5), 1)
choices <- c("t-test", "chi-squared test", "Wilcoxon signed-rank test")

# Inside the exercise body:
# How many observations are in the sample? `r add_cloze(n)`
# What is the sample mean? `r add_cloze(mean_x, tolerance = 0.1, digits = 1)`
# Which method is appropriate? `r add_cloze(choices[1], choices, type = "schoice")`
#
# Meta-information:
# exclozetype: `r format_metainfo("type")`
# exsolution: `r format_metainfo("solution")`
# extol: `r format_metainfo("tolerance")`
```

See the bundled file `stats_cloze.Rmd` for a full, self-contained example.

## Choice questions

Single-choice and multiple-choice questions follow the standard `R/exams`
pattern with `answerlist()` in the question and a logical answer key in the
solution block.

````markdown
Question
========
Which statement about p-values is correct?

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(c(
  "A p-value below 0.05 can justify rejection at the 5% level.",
  "A p-value is the probability that the null hypothesis is true.",
  "A p-value cannot depend on the sample size."
), markup = "markdown")
```

Solution
========
```{r solutionlist, echo = FALSE, results = "asis"}
exams::answerlist(c("True", "False", "False"), markup = "markdown")
```
````

## Points and metadata

If you want imports to arrive with explicit scoring in ILIAS, include
`expoints` in the exercise metadata.

```{r}
Meta-information
================
extype: schoice
exsolution: 100
exname: P-value interpretation
exshuffle: TRUE
expoints: 1
```

For cloze exercises with several gaps, you can provide one point value per gap.
