```{r data generation, echo = FALSE, results = "hide"}
n_a <- sample(18:22, 1)
n_b <- sample(18:22, 1)
mean_a_true <- sample(72:78, 1)
diff_true <- sample(c(-6, -4, 0, 4, 6), 1)
sd_pool <- sample(7:10, 1)

scores_a <- round(rnorm(n_a, mean = mean_a_true, sd = sd_pool), 1)
scores_b <- round(rnorm(n_b, mean = mean_a_true - diff_true, sd = sd_pool), 1)

d <- data.frame(
  group = c(rep("A", n_a), rep("B", n_b)),
  score = c(scores_a, scores_b)
)
write.csv(d, "tutorial_scores.csv", row.names = FALSE, quote = FALSE)

tt <- t.test(score ~ group, data = d, var.equal = TRUE)
mean_a <- mean(scores_a)
diff_ab <- mean(scores_a) - mean(scores_b)
pval <- unname(tt$p.value)
ci_low <- unname(tt$conf.int[1])

test_sol <- c(TRUE, FALSE, FALSE)
interp_sol <- c(pval >= 0.05, pval < 0.05 & diff_ab > 0, pval < 0.05 & diff_ab < 0)
equal_var_sol <- c(TRUE, FALSE)
```

Question
========
A lecturer wants to compare exam scores between two independent tutorial groups.
The file [tutorial_scores.csv](tutorial_scores.csv) contains the variables `group`
and `score`.

How many students are in Group A?
##ANSWER1##

Using the supplied data, compute the mean score of Group A.
##ANSWER2##

Which test is appropriate for comparing the two independent group means here?
##ANSWER3##

What is the p-value of the pooled two-sample t-test?
##ANSWER4##

Does the pooled version of the test assume equal variances in the two groups?
##ANSWER5##

What is the lower endpoint of the 95% confidence interval for A - B?
##ANSWER6##

At the 5% level, which conclusion is correct?
##ANSWER7##

Compute the difference in means A - B.
##ANSWER8##

Answerlist
----------
*
*
* pooled two-sample t-test
* paired t-test
* chi-squared test
*
* Yes
* No
*
* There is no significant mean difference between the groups
* Group A has a significantly higher mean score than Group B
* Group A has a significantly lower mean score than Group B
*

Solution
========
The standard procedure is a pooled two-sample t-test. The pooled version
assumes equal variances in the two groups.

The numerical answers can be obtained in R with:

```{r analysis, echo = FALSE, comment = NA}
aggregate(score ~ group, data = d, mean)
t.test(score ~ group, data = d, var.equal = TRUE)
```

Meta-information
================
exname: Mixed statistics cloze
extype: cloze
exclozetype: num|num|schoice|num|schoice|num|schoice|num
exsolution: `r n_a`|`r fmt(mean_a, 1)`|`r mchoice2string(test_sol)`|`r fmt(pval, 3)`|`r mchoice2string(equal_var_sol)`|`r fmt(ci_low, 2)`|`r mchoice2string(interp_sol)`|`r fmt(diff_ab, 1)`
extol: 0|0.1|0|0.001|0|0.02|0|0.1
